\section{
  \en{Experience}
  \ru{Опыт}
 }
\en{
	\resumeSubHeadingListStart
	\resumeSubheading
	{Quantitative Trader}{Jan 2023 --- Present}
	{ALOR Invest}{Moscow, Russia}

	\resumeSubheading
	{ML Intern}{July 2022 --- June 2023}
	{HSE Robotics Laboratory}{Moscow, Russia}

	\resumeSubheading
	{Freelancer}{Summer 2019, Summer 2020, Summer 2021}{}{}

	\resumeSubHeadingListEnd
}
\ru{
	\resumeSubHeadingListStart
	\resumeSubheading
	{ML стажёр}{Июль 2022 --- Настоящее время}
	{Группа робототехники НИУ ВШЭ}{Москва}

	\resumeSubHeadingListEnd
}

\vskip 5pt

\en{Currently, I work as a Quantitative Trader at ALOR Invest, which is a small HFT fund. My tasks include researching ideas for new trading strategies, implementing them in C++ and carefully tracking their performance. Currently, I am working on improving a market-making strategy. Also, I do some miscellaneous tasks like data conversion and latency analyzis.}
\ru{На данный момент я работаю количественным трейдером в HFT фонде в рамках АЛОР Инвест. Мои основные задачи это исследование идей для новых стратегий, их написание на C++ и отслеживание результатов их работы. Сейчас я работаю над улучшением маркетмейкинг стратегии. Также я занимаюсь и мелкими задачами (конвертация данных, анализ задержек и пр.)}

% \en{As a freelancer, I have developed several Web Crawlers using Beautifulsoup, automated browsers using Selenium and developed a few APIs which involved interactions with SQL databases.}
% \ru{В роли фрилансера я разработал несколько парсеров (пауков/web crawkers) используя Beautifulsoup, автоматизировал браузеры при помощи Selenium, написал API, включающие взаимодействия с реляционными БД}

\vskip 8pt

\en{Also I have been developing several projects for educational purposes for some time now.}
\ru{Также я писал проекты, чтобы изучить новые технологии.}
\en{Here are some of them:}
\ru{Вот некоторые из них:}
\begin{itemize}
	\item \link{https://github.com/NChechulin/cartpole-torch}{Reinforcement Learning in CartPole problem}
	      \en{(In progress)}\ru{(В процессе)} ---
	      \en{Trying to balance a pole on a moving cart using Reinforcement learning. To be precise, we compared the Deep Value Iteration and Deep Deterministic Policy Gradient algorithms' performance under learning time constraints.}
	      \ru{Балансируем стержень, подвешенный на движущейся каретке, при помощи обучения с подкреплением.}

	\item \link{https://github.com/NChechulin/python-yandex-contest-tools}{YandexContest tools} ---
	      \en{An automatic solution checker for a programming contest system with results export.}
	      \ru{Программа для автоматической проверки решений с Yandex Contest с последующим экспортом результатов.}
	      \en{Can detect whether a particular solution uses banned or required Python keywords.}
	      \ru{Включает проверку наличия/отсутствия определенных ключевых слов Python.}

	\item \link{https://github.com/NChechulin/GNN-project}{Topological and Geometric Deep Learning} ---
	      \en{A 2nd year university research project dedicated to learning Graph Neural Networks and ways to modify input data and existing models in order to increase accuracy.}
	      \ru{Исследовательский университетский проект на 2м курсе, посвященный изучению графовых нейросетей и поиску методов улучшения их точности посредством преобразования входных данных или самих моделей.}
\end{itemize}

\en{My other projects can be found on my \link{https://github.com/NChechulin}{GitHub}.}
\ru{Другие проекты есть на моем \link{https://github.com/NChechulin}{Гитхабе}.}
