\documentclass[letterpaper,14pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\newcommand{\link}[2]{{\color{blue}\href{#1}{#2}}}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE Nikolay Chechulin} \\ \vspace{2pt}
    % Backend development intern \\
    \begin{multicols}{2}
    \begin{flushleft}
    \link{https://github.com/NChechulin}{GitHub: NChechulin}\\
    \link{{https://www.linkedin.com/in/nikolay-chechulin-648158202/}}{LinkedIn}
    \end{flushleft}
    
    \begin{flushright}
    Telegram: \link{https://t.me/nchechulin}{@nchechulin} \\
    Email: \link{mailto:nchechulin@aol.com}{nchechulin@aol.com}
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Higher School of Economics}{Sep. 2020 --- Present. Graduation date: July 2024}
      {Data Science and Business Analytics, 2nd year}{Moscow, Russia}
      
      \resumeSubheading
      {School №179}{Sep. 2017 --- June 2020}
      {Engineering class}{Moscow, Russia}
      
      \resumeSubheading
      {Tinkoff Generation}{Sep. 2018 --- January 2020}
      {Algorithms and Data Structures}{Moscow, Russia}

  \resumeSubHeadingListEnd
  \vskip 5pt
  
  During the first year of my studies in pilot (advanced) group I learned fundamentals of Algebra, Calculus, Discrete Mathematics and Linear Algebra, also we devoted more than 6 hours a week to learning academic English.
  Speaking of programming, during the first semester we have been learning basics of Python and Pandas, and during the second -- basics of C++ together with Qt framework.
  
  Here are some relevant grades for the 1st year of studies (10 point scale):
  
  \begin{multicols}{2}
  \begin{itemize}
      \item \textbf{Python} --- 10
      \item \textbf{C++} --- 9
      \item \textbf{Calculus} --- 10, 9, 9 (for 1st, 2nd and 3rd semesters)
      \item \textbf{Discrete Mathematics} --- 9
      \item \textbf{Algorithms and Data Structures} --- 9
      \item \textbf{Best practices in software development} --- 10
      \item \textbf{Probability theory and statistics} --- 8
  \end{itemize}
  \end{multicols}
  
  Speaking of Algorithms and Data Structures, I don't have my grade yet, however, I can claim that I cope with the course successfully.
  

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freelancer}{Summer 2019, Summer 2020, Summer 2021}{}{}
  \resumeSubHeadingListEnd
  
  \vskip 5pt
      
  I have developed several Web Crawlers using Beautifulsoup, automated browsers using Selenium and developed a few API's which involved interactions with SQL databases.
  
  \vskip 8pt
  
  Also I have been developing several projects for educational purposes since 2019.
  Here are some of them:
  \begin{itemize}
    \item \link{https://github.com/NChechulin/GNN-project}{Topological and Geometric Deep Learning (in progress)} --- A university research project dedicated to learning Graph Neural Networks and ways to modify input data and existing models in order to increase accuracy.
    
    \item \link{https://github.com/NChechulin/python-yandex-contest-tools}{YandexContest tools} --- an automatic solution checker for a programming contest system.
    Can detect whether a particular solution uses banned or required Python keywords.
    
    \item \link{https://github.com/NChechulin/tim}{Tim --- ToDo improved} --- a simple CLI ToDo application implemented in Rust
    
    \item \link{https://github.com/NChechulin/evolution-of-cells}{Evolution of cells} -- \textbf{(In development, unfinished)} My attempts to research what random occasional mutations can do with a group of cells.
    Heavily inspired by a \link{https://www.youtube.com/watch?v=SfEZSyvbj2w&list=PLnmlxA5EUR3F4BrpqTl0koT5Cx5aXjBIA}{YouTube series} on genetic algorithm by Foo52ru.
    
    \item \link{https://github.com/NChechulin/url-shortener-api}{URL Shortener} --- A Flask API for self-hosted URL shortening service.
    
    \item \link{https://github.com/NChechulin/apsolutions-intern-test-task}{Text search API} --- A Flask API which provides a full-text search over some given data. The project initially has been a test task.
    
    \item \link{https://github.com/NChechulin/wiki-game-telegram-bot}{Wiki Game bot} --- A Telegram bot which finds a path from a given Wikipedia article to another preselected article.
    
    \item \link{https://github.com/NChechulin/markov-chain-telegram-bot}{Markov chain bot} --- A small telegram bot which generates responses using Markov Chain. Implemented in Rust.
    
  \end{itemize}
  
  My other projects can be found on my \link{https://github.com/NChechulin}{GitHub}.

% %-----------PUBLICATIONS-----------
% \section{Publications}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%     \textbf{New techniques for Elektronik supersonik laser shootings. WORKSHOP ON INDUSTRY APPLICATION - Molvanîan Academy o Science, 2020 . p. 225-231.}{\\J. Zlad Doe}\\
%         \textbf{Space Rockets . WORKSHOP ON INDUSTRY APPLICATION - Molvanîan Academy o Science, 2021 . p. 25-31.}{\\J. Zlad Doe, Darth Vapor}\\
% \ 
% }}
%  \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills, Language Skills, and Interests}
%  \begin{itemize}[leftmargin=0.15in, label={}]
    % \item{
    \textbf{OS}{: GNU/Linux (primary), Windows} \\
    \textbf{Programming Languages}{: Python \textit{(primary one)}, basics of SQL, C\# for desktop development, C++ and basics of Rust} \\
    \textbf{Libraries}{: Pandas, Numpy, Flask, Selenium, QT, Beautifulsoup}\\
    \textbf{Version Control}{: Git} \\
    \textbf{Writing}{: LaTeX, Markdown, LibreOffice, Microsoft Office} \\
    \textbf{Soft skills}{: Fast learner, good communicator, responsible employee} \\
    \textbf{Languages}{: Russian (native), English (IELTS Academic 8.0, C1)} \\
    \textbf{Interests}{: Free \& Open Source software, Road cycling, Rust, Learning English}
    % }
%  \end{itemize}

% %-----------CERTIFICATIONS-----------
% \section{Extracurricular}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Specialization}{:\href{certification site}{ Course} } 
%     }}
%  \end{itemize}

\end{document}

